---
title: "Simple document"
author: "Jeff Goldsmith"
date: 2024-09-12
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---
usethis::use_git_config(user.name = "Mingye Xie", user.email = "williamxie0809@gmail.com")

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

```{r plot_example, collapse=TRUE}
library(tidyverse)

plot_df =tibble(
  x=rnorm(500, mean = 2, sd = 4),
  y = 3-4.2*x +rnorm(500)

  )

ggplot(plot_df, aes (x=x, y=y))+geom_point()
```

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell